---
title: "ChurnPrevention"
author: "TriDoan"
date: "April 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a simulate customer churn retention project

The purpose of Churn prevention is a measure to ensure that customers visit the online shop again.

```{r }

setwd('C:/Projects_simulate/Marketing_analytics')

library(dplyr)
library(ggplot2)
library(corrplot)

defaultData <- read.csv("defaultData.csv", header=TRUE, sep=";")

```

0. Explore data
```{r}
# Summary of data
summary(defaultData)

# Look at data structure
str(defaultData)

# Analyze the balancedness of dependent variable
ggplot(defaultData,aes(x = PaymentDefault)) +
  geom_histogram(stat = "count") 

```

1. Using glm model to built logistic regression

```{r}
# Build logistic regression model
logitModelFull <- glm(PaymentDefault ~ limitBal + sex + education + marriage +
                   age + pay1 + pay2 + pay3 + pay4 + pay5 + pay6 + billAmt1 + 
                   billAmt2 + billAmt3 + billAmt4 + billAmt5 + billAmt6 + payAmt1 + 
                   payAmt2 + payAmt3 + payAmt4 + payAmt5 + payAmt6, 
                family = binomial, data = defaultData)

# Take a look at the model
summary(logitModelFull)

# Take a look at the odds
coefsexp <- coef(logitModelFull) %>% exp() %>% round(2)
coefsexp

```

3. Implement model selection

```{r}
library(MASS)
# The old (full) model
logitModelFull <- glm(PaymentDefault ~ limitBal + sex + education + marriage +
                   age + pay1 + pay2 + pay3 + pay4 + pay5 + pay6 + billAmt1 + 
                   billAmt2 + billAmt3 + billAmt4 + billAmt5 + billAmt6 + payAmt1 + 
                   payAmt2 + payAmt3 + payAmt4 + payAmt5 + payAmt6, 
                 family = binomial, defaultData)

#Build the new model
logitModelNew <- stepAIC(logitModelFull,trace=0) 

#Look at the model
summary(logitModelNew) 

# Save the formula of the new model (it will be needed for the out-of-sample part) 
formulaLogit <- as.formula(summary(logitModelNew)$call)
formulaLogit

```
4. Evaluate model

``{r}
# Make predictions using the full Model
defaultData$predFull <- predict(logitModelFull, type = "response", na.action = na.exclude)

# Construct the in-sample confusion matrix
confMatrixModelFull <- confusion.matrix(defaultData$PaymentDefault,defaultData$predFull, threshold = 0.5)
confMatrixModelFull

# Calculate the accuracy for the full Model
accuracyFull <- sum(diag(confMatrixModelFull)) / sum(confMatrixModelFull)
accuracyFull

```
5. Compare simple and full model

 Calculate the accuracy for 'logitModelNew'



```{r}
# Construct the in-sample confusion matrix
library(SDMTools)
logitModelNew <- glm(formula = PaymentDefault ~ marriage + pay1 + pay3 + pay5 + 
    billAmt1 + billAmt6 + payAmt1 + payAmt2 + payAmt5 + payAmt6, 
    family = binomial, data = defaultData)

# Calculate the accuracy for 'logitModelNew'

defaultData$predNew <- predict(logitModelNew, type = "response", na.action = na.exclude)


# Construct the in-sample confusion matrix
confMatrixModelNew <- confusion.matrix(defaultData$PaymentDefault,defaultData$predNew, threshold = 0.5)
confMatrixModelNew

accuracyNew <- sum(diag(confMatrixModelNew)) / sum(confMatrixModelNew)
accuracyNew

```
Determine optimal threshold

```{r}
# Prepare data frame with threshold values and empty payoff column
payoffMatrix <- data.frame(threshold = seq(from = 0.1, to = 0.5, by = 0.1),
                           payoff = NA) 
payoffMatrix 
 
for(i in 1:length(payoffMatrix$threshold)) {
  # Calculate confusion matrix with varying threshold
  confMatrix <- confusion.matrix(defaultData$PaymentDefault,
                defaultData$predNew, 
                threshold = payoffMatrix$threshold[i])
  # Calculate payoff and save it to the corresponding row
  payoffMatrix$payoff[i] <- confMatrix[2,2]*1000 + confMatrix[2,1]*(-250)
}
payoffMatrix

```
7. Evaluate iwth out of sample

```{r}
# Split data in train and test set
set.seed(534381) 
defaultData$isTrain <- rbinom(nrow(defaultData), 1, 0.66)
train <- subset(defaultData, defaultData$isTrain == 1)
test <- subset(defaultData, defaultData$isTrain  == 0)

logitTrainNew <- glm(formulaLogit, family = binomial, data = train) # Modeling
test$predNew <- predict(logitTrainNew, type = "response", newdata = test) # Predictions

# Out-of-sample confusion matrix and accuracy
confMatrixModelNew <- confusion.matrix(test$PaymentDefault, test$predNew, threshold = 0.3) 
sum(diag(confMatrixModelNew)) / sum(confMatrixModelNew) # Compare this value to the in-sample accuracy

